---
title: "Twitter_API_With_R"
author: "Jeff Kropelnicki"
date: "4/26/2017"
output: github_document
---

In this R markdown I will be learning to use the twitter API and running some tests. I am doing this for a class at the University of Minnesota: Health	Data Analytics and Data Science.    
   
   
```{r, warning=FALSE, message=FALSE}
install.packages("httpuv")
library("rtweet") #package for getting data from twitter. 
library("dplyr")
```   
   
      
Creating a token
```{r, message=FALSE}
# appname, consumer_key, consumer_secret created in a different R script so that they are not shared with the world.

#https://apps.twitter.com/app/13722867/keys

twitter_token <- create_token( app = appname,
    consumer_key = consumer_key,
    consumer_secret = consumer_secret)
```   
   
Getting data from twitter and adding to new data frame.  
```{r}
rstats <- search_tweets("#rstats", n=1000)
names(rstats)

hist(rstats$created_at, breaks=60, freq=TRUE) 
```   
Looking at the histagram it is interesting to see that the hashtag is being used all day, I returned 982 tweets with the hashtag rstats in just over 24 hours.    
   
Who is using the hashtag?   
```{r}
who <- rstats %>% group_by(screen_name) %>% summarise(count = n()) %>% arrange(desc(count))
```

   








