---
title: "Twitter_API_With_R"
author: "Jeff Kropelnicki"
date: "4/26/2017"
output: github_document
---

In this R markdown I will be learning to use the twitter API and running some tests. I am doing this for a class at the University of Minnesota: Health	Data Analytics and Data Science.    
   
Interesting link using R to download and save images from twitter. 
https://jasdumas.github.io/2017-05-02-twitter-ml-flashcards/?utm_content=buffer04c06&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer   
   
```{r, warning=FALSE, message=FALSE}
install.packages("httpuv")
library("rtweet") #package for getting data from twitter. 
library("dplyr")
library(magick) #open-source image processing library available
library(stringr)
library(kableExtra) #functions to help build complex HTML or 'LaTeX'
library(knitr)
```   
   
      
Creating a token
```{r, message=FALSE}
# appname, consumer_key, consumer_secret created in a different R script so that they are not shared with the world.

twitter_token <- create_token( app = appname,
    consumer_key = consumer_key,
    consumer_secret = consumer_secret)
```   
   
Getting data from twitter and adding to new data frame.  
```{r}
tweets <- search_tweets("#machinelearningflashcards", n=500, include_rts = FALSE) %>% filter(screen_name == 'chrisalbon')
```   
   
 
```{r}
mt <- tweets[1:3, 1:5]

kable(tweets, format = "html") %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = F)
```   
   
Get the text within the tweet to add to the file name by removing the hash tag and URL link with some light regex:   
   
```{r}
tweets$clean_text <- tweets$text
tweets$clean_text <- str_replace(tweets$clean_text,"#[a-zA-Z0-9]{1,}", "") # remove the hashtag
tweets$clean_text <- str_replace(tweets$clean_text, " ?(f|ht)(tp)(s?)(://)(.*)[.|/](.*)", "") # remove the url link
tweets$clean_text <- str_replace(tweets$clean_text, "[[:punct:]]", "") # remove punctuation
```   
   
Write a function to download images of the flashcards from the media_url column and append the file name from the cleaned tweet text description and save into a folder:   
   
   
```{r}
save_image <- function(df){
  for (i in c(1:nrow(df))){
    image <- try(image_read(df$media_url[i]), silent = F)
  if(class(image)[1] != "try-error"){
    image %>%
      image_scale("1200x700") %>%
      image_write(paste0("/Users/jeffkropelnicki/Desktop/tweets", tweets$clean_text[i],".jpg"))
  }
 
  }
   cat("Function complete...\n")
}
```   
   
Apply the function:   
   
```{r}
save_image(tweets)
```





   








